---
title: "PredictionAssignmentWriteup"
output:
  html_document: default
  pdf_document: default
---

```{r}
knitr::opts_chunk$set(echo = TRUE)
```

This exercise observes human acticity collected using smart divices. We would study the patterns from testing dataset.

##Data Cleaning
The testing datasets contains raw data of 20 user's exercise activities and measured 125 variables.
We need to load the data first and exclude all NAs.

```{r}
pmlTrain<-read.csv("pml-training.csv", header=T, na.strings=c("NA", "#DIV/0!"))
pmlTest<-read.csv("pml-testing.csv", header=T, na.string=c("NA", "#DIV/0!"))
# exclude NAs from dataset
noNApmlTrain<-pmlTrain[, apply(pmlTrain, 2, function(x) !any(is.na(x)))] 
dim(noNApmlTrain)
# remove user information and time other irrelevant variables
finalpmlTrain<-noNApmlTrain[,-c(1:8)]
dim(finalpmlTrain)
```

```{r}
# data for validation
finalpmltest<-pmlTest[,names(finalpmlTrain[,-52])]
dim(finalpmltest)
```

# Data Patitioning
In this simulation, we will include 80% data from training data and 20% from testing data
```{r}
library(caret)
patitioning<-createDataPartition(y=finalpmlTrain$classe, p=0.8,list=F)
DataTraining<-finalpmlTrain[patitioning,] 
DataTest<-finalpmlTrain[-patitioning,] 
dim(DataTraining)
dim(DataTest)
```

```{r}
set.seed(133)
```

```{r}
fitControl2<-trainControl(method="cv", number=5, allowParallel=T, verbose=T)
rffit<-train(classe~.,data=DataTraining, method="rf", trControl=fitControl2, verbose=F)
predrf<-predict(rffit, newdata=DataTest)
confusionMatrix(predrf, DataTest$classe)
```
from the results above we learn that the accuracy for 5 fold cross validation is 99.31%.
The 95% condidence interval is [0.99,0.9955] and Kappa equal to 0.9913.

# Predictions
```{r}
# predits 20 cases
pred20<-predict(rffit, newdata=finalpmltest)
pred20
```
